Top Text

### 2022-12-13 Paper.tex
commit

In figure 5 we see it has the most iterations out of any of the other applications. When comparing the amount of iterations that each subject has in both figure on and figure two, these two applications are very close.(-This can be attributed to the fact that the amount of experience with these graphs is very similar for both subjects-)

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth]{Bargraph}
	\caption{}
	\label{fig:bargraph}
\end{figure}
\pagebreak
\subsection{Figure 7}
Figure 5 shows that the average distances of all the applications from broth subjects one and two are very close.(this is due to the random nature of t-i-g and shows that a good application is more judged by the functionality it offers rather than its algorithm when it comes to new comers). When comparing the applications Dall-E has the least average distance and stable diffusion has the most average distance but again only by a slight margin.

@@

	In Figure 8 there are two important points of interest. Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between q2 and q3. This means the spread of the distances is also the largest out of any of the other applications. Second is that Stable Diffusion has the largest median distance. Mention something about the outliers.

@@

	During the course of this research we were able to prove the legitimacy of our secondary research question. This was done by a analysing figures two through to six. The applications shown in figure two and three are applications that both subjects have experience in(Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion). What makes figure two and three important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate.

	In figure three and four we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in. using comparative analysis we can then compare both the graphs that the users have experience in (being figure two and three ) and the graphs that the subjects don't have experience in ( being figure four and five ) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together.

	When we take a look at figure six we can see that even though even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars in very small. This can be attributed to the nature of text-to-image generation being that of a random series of attempt until the user reaches a point where they are happy with the picture. This is further proven when you look at any of the patterns for figures 2 through 5 and how the distance for each iterations follows no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations.

	\subsection{Secondary research question justification}

	In order to answer the secondary research question we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of an of generated images with inexperienced users which makes sense as they may struggle to use said functionality(! add section on ease of use Stable diffusion we looking at you -This however only applies for artists who are already experienced, because it can take quite some practice to get used to all the tools that are available in stable diffusion. We expect inexperienced artists to struggle finding the right settings because of the amount of freedom they get. In the case of a completely inexperienced artist, they might find Dall-E or Midjourney easier to use because they can create photo-realistic results without having to fine tune any settings apart from the prompt.-). This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users.

	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generations technique is because AI text-to-image generation is very random and relies a lot on luck even for users that are experienced with applications. What we do know is that if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make the faster you are more likely to get the result you are looking for.

@@

	Our primary research question can then be answered now that we know what makes a good ai text-to-image application and that is how fast the application is able to generate iterations. With this in mind we can then say that Dall-E has the most iterations. It also offers a very streamline user experience and is easy to access and intuitive to use.

>>>>

In figure 5 we see that Dall-E has the most iterations out of any of the other applications. When comparing the amount of iterations that each subject has in both figure 3 for Stable diffusion and figure 4 for Midjourney, the two applications are very far apart. In contrast the amount of iterations between each subject is very close together in figure 5 for Dall-E and figure 6 for Dream by Wombo.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth]{Bargraph}
	\caption{}
	\label{fig:bargraph}
\end{figure}
\pagebreak
\subsection{Figure 7}
Figure 5 shows that the average distances of all the applications from both subjects one and two are very close. When comparing the applications Dall-E has the least average distance and stable diffusion has the most average distance but again only by a slight margin.

@@

	In Figure 8 there are two important points of interest. Firstly is that Dall-E has a massive range between the minimum and maximum distances when compared to the other applications as well as having the largest space between quartile 2 and quartile 3. This means the spread of the distances is also the largest out of any of the other applications. Second is that Stable Diffusion has the largest median distance.

@@

	In order to find the best application out of the four we chose we needed to see what actually makes a text-to-image generation application good. This was done by a analysing figures 3 through to 7. The applications shown in figure 3 and 4 are applications that both subjects have experience in (Subject 1 has experience with Midjouney and Subject 2 has experience with Stable diffusion). What makes figure 3 and 4 important is that both the graphs show the difference that having experience in an application makes, and that difference is only in the amount of iterations the user is able to generate because the quality of the images is very random which can be seen with how the line graphs from figures 3 to 6 all fluctuate hugely and never set any kind of discernible pattern.

	In figure 5 and 6 we then see two applications that neither Subject 1 nor Subject 2 have any prior experience in. using comparative analysis we can then compare both the graphs that the users have experience in (being figure 3 representing Stable diffusion and 4 representing Midjourney) and the graphs that the subjects don't have experience in ( being figure 5 representing Dall-E and 6 representing Dream by Wombo) and we can see more clearly that when both subjects have the same amount of experience with an applications the amount of iterations the subjects are able to generate is noticeably closer together compared to when there is a discrepancy in experience level.

	When we take a look at figure 7 we can see that even though it is the combinations of the averages of all iterations across both Subject 1 and 2 per application, the differences between the bars is very small. This can be attributed to the nature of text-to-image generation being that of a random series of attempts until the user reaches a point where they are happy with the result. This is further proven when you look at any of the patterns for figures 3 through 6 and how the distance for each application's iterations follow no solid pattern but rather jumps around sometimes even ending up further away from the original image than some of the earlier iterations. An example of this can be seen in figure 4 with Subject 1.

	\subsection{Answering secondary research question}

	In order to answer the secondary research question we looked at how different aspects of the applications affected the resulting images that were generated and came to the conclusion that the amount of functionality does not play a role in the quality of generated images with inexperienced users which makes sense as they may struggle to use said functionality.This can be seen when you take into consideration that stable diffusion has the most functionality but it has the worst average iteration quality across both users. 
	We also looked at how easy the application was to gain access to and came to the conclusion that every one of them was very easy to use and gain access to, so that also became an irrelevant comparison factor.

	With all this information we can now say that an application's value to an inexperienced user is not about how good the AI generation technique is nor is it about how much functionality it supplies it's user. This is because AI text-to-image generation is very random and relies a lot on luck with our current technology even for users that are experienced with these applications. What we do know is that currently if all the applications rely on luck to some degree it is then better if the application is able to give many iterations because the more attempts you are able to make, the faster you are more likely to get the result you are looking for.

@@

	Our primary research question can then be answered now that we know what makes an AI text-to-image application good for an inexperienced user and that is how fast the application is able to generate iterations. With this in mind we can then say that the best application out of the four we chose is Dall-E as it is able to generate the most iterations. On a side note our experience with it also lead to us believing that it offers a very streamline user experience, is easy to access and intuitive to use.
